### 2021-06-09 setup.tex
R2-C4

In the second study 
we investigate whether or not a more advanced static analysis approach is promising for
identifying malwares, given a version of an app that is proved to be secure.
To this end, we leverage the FlowDroid
taint analysis algorithms for Android apps, in order to identify paths between
\emph{sources} and \emph{sinks}. In this case,
our goal is to investigate if it is possible to detect malicious
behavior by identifying the divergent source-sink paths that FlowDroid finds in the
benign / malign versions of the Android apps.

Concerning this second study, a \emph{hit} occurs whenever
FlowDroid finds an additional source-sink path in the malicious version of an app.
Our goal is to answer our third research question using this approach. We use two metrics in this second study:
the total number of malicious apps FlowDroid is able to find and the
execution time for running the taint analysis algorithm for each app.
In this second study we use the same dataset of $96$ pairs of Android apps (B/M),
originally shared in the AndroZoo repository~\cite{DBLP:conf/msr/AllixBKT16} and
also used in the \blls.

We conduct this investigation in three steps. First, we define
the set of API calls considered as \emph{source of sensitive information} (e.g.,
a method that access the address book) or
that \emph{might share information} (e.g., a method that sends messages
to external peers). We rely on a the source-sink definitions of a previous
study~\cite{}. After defining the sources and sinks of interest,
we run FlowDroid to mine the source-sink paths from each benign app, and then enumerate the
possible data flows between sources and sinks. These paths are considered valid in
our analysis. Next, we repeat the the FlowDroid execution considering the malicious version
of the apps. In the final step, we compare the sets of source-sink paths between the benign and malicious
version of an app, in order to reveal the existence of additional paths in the
malicious version.

\begin{figure}
\includegraphics[scale=0.3]{images/second-study-settings.pdf}
\end{figure}

>>>>

In the second study 
we investigate whether or not a more advanced static analysis approach is promising for
identifying malwares, given a version of an app that is proved to be secure.
To this end, we leverage the FlowDroid
taint analysis algorithms for Android apps, in order to identify dataflows
that might lead to the leakage of sensitive information. Our
goal here is to investigate if it is possible to detect malicious
behavior by identifying the \emph{divergent} source-sink paths that FlowDroid reveals after
analysing a benign and a malign versions of an Android app.
define.

FlowDroid takes as input an Android Application Package (APK file) and
a set of API methods marked either as {\bf source}
or {\bf sink}. Source methods are those that access \emph{sensitive information} (e.g.,
a method that access the address book), while sink methods are those 
that \emph{might share information with external peers} (e.g., a method that
sends messages to a recipient). We rely on the source-sink definitions of a previous
study~\cite{}, which involves ABC source methods and XYZ sink methods.
FlowDroid then uses a \emph{context, flow, and field
sensitive analysis} to identify all dataflow paths from sources to sinks~\cite{}.
However, it is important to note that not all source-sink paths are malicious, and then we
follow a specific methodology to identify malwares in our work: we raise a
warning (a \emph{hit}) whenever
FlowDroid finds an additional source-sink path in the malicious version of an app, which
has not been identified when analysing the benign version.

Our research settings involve three steps (see Figure~\ref{fig:settings2}).
In the first, we execute FlowDroid to mine the source-sink paths from a
benign version of an app, and then enumerate a set (S1) with the 
possible dataflows between sources and sinks. All paths in S1 are considered safe in
our analysis. In the second step we repeat the FlowDroid execution, though
considering the malicious APK version of the app. This leads to a second set (S2) of source-sink paths. In the final step, we compute the difference (S3) between
the sets S2 and S1 (i.e., $S3 = S2 \setminus S1$), in order to reveal
the existence of additional paths in the
malicious version. If the set S3 is not empty, we conclude that FlowDroid
identified the malware.

We use two metrics in this second study:
the total number of malicious apps FlowDroid is able to find and the
execution time for running the taint analysis algorithm for each app.
Moreover, in this second study we use the same dataset of $96$ pairs of Android apps (B/M),
originally shared in the AndroZoo repository~\cite{DBLP:conf/msr/AllixBKT16} and
also used in the \blls.

\begin{figure}
  \centering{\includegraphics[scale=0.4]{images/second-study-settings.pdf}}
  \caption{Overview of our approach in the second study.}
  \label{fig:settings2}
\end{figure}
